Predicting and Preventing Employee Turnover through HR Analytics

### 2024-06-07 products/manuscript/Manuscript.qmd
.

hr_data = read.csv("C:/Users/crew_/OneDrive/Escritorio/Guille/UTSA Masters/MSDA/DA6833/PracticumII-Course/guillermogallardo-final-project/data/raw-data/IBM HR Analytics Data.csv", header = TRUE)
```

>>>>

hr_data = read.csv("C:/Users/crew_/OneDrive/Escritorio/Guille/UTSA Masters/MSDA/DA6833/PracticumII-Course/guillermogallardo-final-project/data/raw-data/IBM HR Analytics Data.csv", header = TRUE) #not synced with OneDrive but my computer added that folder when I entered my email when I bought the computer
```
